Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-02-26 apples_and_oranges.qmd
Added code for looking and gender and age

# # Now CBT studies
# 
# cbt_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt",]$new_study_id
# 
# cbt_studies_baseline_metareg <- all_studies_baseline_metareg %>%
#   filter(new_study_id %in% cbt_study_ids) %>% 
#   filter(!(arm_effect_size == "cohens_d_active" & !(type == "cbt")))
# 
# 
# #turn sds to sec
# cbt_studies_baseline_metareg$baseline_stand_error <- cbt_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(cbt_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# cbt_studies_baseline_metareg$baseline_mean <- cbt_studies_baseline_metareg$perc_baseline_mean
# results_cbt_studies_baseline_metareg <- run_metareg_and_extract(cbt_studies_baseline_metareg,  
#                                                          model_1, condition)

@@

met_perc_women <- metagen(TE = percent_women,
                           seTE = percent_women_std_error,
                           studlab = new_study_id,
                           data = df_for_gender_metan,
                           sm = "SMD",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "percentage women across studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)
met_perc_women

@@

met_age <- metagen(TE = mean_age,
                           seTE = sd_age / sqrt(baseline_n),
                           studlab = new_study_id,
                           data = df_for_age_metan,
                           sm = "SMD",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "age across studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)

>>>>

@@

met_perc_women <- metagen(TE = percent_women,
                           seTE = percent_women_std_error,
                           studlab = new_study_id,
                           data = df_for_gender_metan,
                           sm = "",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "percentage women across studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)
met_perc_women

# looking at clinical sample only

df_for_gender_metan_clin <- df_for_gender_metan %>%
  filter(new_study_id %in% clin_study_ids)

met_perc_women_clin <- metagen(TE = percent_women,
                           seTE = percent_women_std_error,
                           studlab = new_study_id,
                           data = df_for_gender_metan_clin,
                           sm = "",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "percentage women across clinical studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)
met_perc_women_clin

@@

met_age <- metagen(TE = mean_age,
                           seTE = sd_age / sqrt(baseline_n),
                           studlab = new_study_id,
                           data = df_for_age_metan,
                           sm = "",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "age across studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)

# looking at clinical sample only

df_for_age_metan_clin <- df_for_age_metan %>%
  filter(new_study_id %in% clin_study_ids)

met_age <- metagen(TE = mean_age,
                           seTE = sd_age / sqrt(baseline_n),
                           studlab = new_study_id,
                           data = df_for_age_metan_clin,
                           sm = "",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "age across clinical studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)
